Reproducable Research Peer Assessment 1: Activity Monitoring
========================================================
This assignment is to analyze the Activity Monitoring dataset
-------------------------------------------------------------

**First, I need to read in the data, and format the Date column as a date:**
```{r, echo=TRUE}
data <- read.csv("activity.csv")
data$Date <- as.POSIXlt(data$date)
```

**Create a Histogram of the total number of steps taken each day (excluding NA's), and caclulate Mean & Median:**
```{r, echo=TRUE}
## Make a histogram of steps, and calculate mean, median:
totalSteps <- aggregate(steps ~ date, data = data, sum, na.rm=TRUE)
hist(totalSteps$steps, col="blue", xlab="Steps Taken", main="Histogram of Steps Taken")
mean <- round(mean(totalSteps$steps),1)
median <- median(totalSteps$steps)
```
**The Mean number of steps taken each day is `r mean`, and the Median is `r median`.**

Plot the mean daily steps taken per interval:
---------------------------------------------
```{r, echo=TRUE}
## Calculate steps per Interval:
intervalSteps <- aggregate(steps ~ interval, data = data, FUN="mean", na.rm=TRUE)
## Make Plot:
plot(steps ~ interval, data=intervalSteps, type="l", xlab = "Interval", ylab = "Steps", main="Avg Steps Taken by Interval:")

## Find the interval with the highest mean steps:
max <- intervalSteps[which.max(intervalSteps$steps),]$interval
```

**The interval of time with the most Avegerage number of steps is interval `r max`.**

Count the number of Missing Values and fill them in:
----------------------------------------------------

```{r, echo=TRUE}
## Find the number of NA's in the dataset:
missing <- sum(is.na(data$steps))
```
**The number of missing values in the dataset is: `r missing`**

```{r, echo=TRUE}
## Fill in NA's with mean of that interval (in new dataset called "Fdata"):
Fdata <- data
nas <- 0
for(i in 1:length(data$steps)) {
      if(is.na(Fdata[i,1]) == TRUE){
            int <- Fdata[i,3]
            avg <- intervalSteps[intervalSteps$interval == int,2]
            Fdata[i,1] <- avg
            nas <- nas + 1
      } 
}
```
**There were `r nas` missing values**

New Histogram:
--------------
**Here is a new histogram of number of steps using the imputed data:**
```{r, echo=TRUE}
## Make a new histogram of steps, and calculate new mean, median (use Fdata):
totalSteps2 <- aggregate(steps ~ date, data = Fdata, sum)
hist(totalSteps2$steps, col="red", xlab="Steps Taken", main="New Histogram of Steps Taken (with Imputed Data)")
mean2 <- round(mean(totalSteps2$steps),1)
median2 <- median(totalSteps2$steps)
```
**Using the imputed data, the new mean is `r mean2`, and the new median is `r median2`.**  
**That is compared to the original mean of `r mean` and original median of `r median`.  **

**Those values are the same, even with the imputed data.**

Plot by Weekend/Weekday:
------------------------

```{r, echo=TRUE}
## Create new columns in Fdata for day of week, and the weekend Factor variable:
Fdata$dow <- weekdays(Fdata$Date, abbreviate=TRUE)
Fdata$dayType <- factor(c("weekday", "weekend"))

## Go throuh the file and indicate whether each date is weekend or weekday:
for(i in 1:length(Fdata$dow)) {
      if(Fdata$dow[i] %in% c("Sat", "Sun")){
            Fdata[i,6] <- "weekend"
      } else {
            Fdata[i,6] <- "weekday"
      }
}
Fdata$dayType <- as.factor(Fdata$dayType)
#Fdata$interval <- as.factor(Fdata$interval)
library("plyr")
library("lattice")
## Make new Intervals data:
intervalSteps2 <- aggregate(steps ~ interval + dayType, Fdata, "mean")
xyplot(steps ~ interval | factor(dayType), data = intervalSteps2, aspect = 1/2, type="l")
```

