Reproducable Research Peer Assessment 1: Activity Monitoring
========================================================
**This assignment is to analyze the Activity Monitoring dataset.**


**First, I need to read in the data, and format the Date column as a date:**
```{r, echo=TRUE}
data <- read.csv("activity.csv")
data$Date <- as.POSIXlt(data$date)
```

**Create a Histogram of the number of steps taken each day (excluding NA's), and caclulate Mean & Median:**
```{r, echo=TRUE}
## Make a histogram of steps, and calculate mean, median:
hist(na.omit(data$steps), col="blue", xlab="Steps Taken", main="Histogram of Steps Taken")
mean <- round(mean(na.omit(data$steps)),2)
median <- median(na.omit(data$steps))
```
**The Mean number of steps taken each day is `r mean`, and the Median is `r median`.**

**Plot the mean steps taken per interval:**
```{r, echo=TRUE}
#df <- data.frame(interval)
Cdata <- na.omit(data)
## Take the mean of each interval and save to dataframe:
intAvg <- tapply(Cdata$steps, Cdata$interval, mean, na.rm=TRUE, simplify=FALSE)
intAvg <- as.data.frame(intAvg, col.names = c("Interval","Steps"))
intAvg <- cbind(row.names(intAvg),intAvg)
names(intAvg)<- c("interval","Steps")

## Change Datatypes:
intAvg$Steps <- as.numeric(intAvg$Steps)
intAvg$interval <- as.numeric(levels(intAvg$interval))[intAvg$interval]

## Make Plot:
plot(intAvg$interval, intAvg$Steps, type="l", xlab = "Interval", ylab = "Steps", main="Avg Steps Taken by Interval:")
# qplot(intAvg$interval, intAvg$Steps, geom="line", xlab = "Interval", ylab = "Steps")
# qplot(interval, Steps, data=intAvg, geom="line", xlab = "Interval", ylab = "Steps") 


## Find the interval with the highest mean steps:
max <- intAvg[intAvg$Steps == max(intAvg$Steps), ]
maxInterval <- max[1,1]
```
**The interval of time with the most Avegerage number of steps is interval `r maxInterval` with an average of `r max[1,2]` steps.**

```{r, echo=TRUE}
## Find the number of NA's in the dataset:
missing <- length(which(is.na(data$steps)))
```
**The number of missing values in the dataset is: `r missing`**

```{r, echo=TRUE}
## Fill in NA's with mean of that interval (in new dataset called "Fdata"):
Fdata <- data
for(i in 1:length(data$steps)) {
      if(is.na(Fdata[i,1]) == TRUE){
            int <- Fdata[i,3]
            avg <- intAvg[(intAvg$interval == int),2]
            Fdata[i,1] <- avg
      } 
}
```
**Here is a new histogram of steps using the imputed data:**
```{r, echo=TRUE}
## Make a new histogram of steps, and calculate new mean, median (use Fdata):
hist(Fdata$steps, col="red", xlab="Steps Taken", main="New Histogram of Steps Taken (with Imputed Data)")
Fmean <- round(mean(Fdata$steps),2)
Fmedian <- median(Fdata$steps)
```
**Using the imputed data, the new mean is `r Fmean`, and the new median is `r Fmedian`.**  
**That is compared to the original mean of `r mean` and original median of `r median`.  **

**Those values are the same, even with the imputed data.**

```{r, echo=TRUE}
## Create new columns in Fdata for day of week, and the weekend Factor variable:
Fdata$dow <- weekdays(Fdata$Date, abbreviate=TRUE)
Fdata$weekend <- factor(c("weekday", "weekend"))

## Go throuh the file and indicate whether each date is weekend or weekday:
for(i in 1:length(Fdata$dow)) {
      if(Fdata$dow[i] %in% c("Sat", "Sun")){
            Fdata$weekend <- "weekend"
      } else {
            Fdata$weekend <- "weekday"
      }
}
Fdata$weekend <- as.factor(Fdata$weekend)
Fdata$interval <- as.factor(Fdata$interval)
library("plyr")
## Make new Intervals data:
#FintAvg <- tapply(Fdata$steps, list(Fdata$interval,Fdata$weekend), mean, simplify=FALSE)
FintAvg <- ddply(Fdata, c("interval","weekend"), summarize, mean=mean(steps))
FintAvg <- aggregate(x=Fdata$steps, by=list(Fdata$weekend, Fdata$interval), FUN=mean)

FintAvg <- as.data.frame(FintAvg, col.names = c("Interval","Steps", "weekend"))
FintAvg <- cbind(row.names(FintAvg),FintAvg)
names(FintAvg)<- c("interval","Steps", "weekend")


## Change Datatypes:
FintAvg$Steps <- as.numeric(FintAvg$Steps)
FintAvg$interval <- as.numeric(levels(FintAvg$interval))[FintAvg$interval]

## Make Plot:
library("lattice")
# plot(Steps ~ interval | weekend, data=FintAvg, layout=c(2,1))
#plot(FintAvg$interval, intAvg$Steps, type="l", xlab = "Interval", ylab = "Steps", main="Imputed Data")
